### 2018-02-07 results.tex
modified figures 5, 6, 7 for results section. pending to modify text
work in progress update

As explained in the methodology, the first step is to subject the dataset through a clustering process to properly label the data according to the classes to be used by the decision tree algorithm. Figure \ref{fig:clusters} presents a sample of the results obtained after the clustering process is completed. Because visual representation above 3 dimensions is not possible, in this figure we limit ourselves to present two-dimensional subspaces, i.e., subspaces for two features (or metrics). Recall that there are 55 subspaces with 2 features, and a total of 550 for the sum of the subspaces with 2, 3, and 4 features.

In particular, Fig.~\ref{fig:clusters} shows six subspaces for an ordered sequence of metric pairs from C1 to C11 (see Table \ref{tab:metrics}). Although it would be impractical to discuss all the possible combinations, some points can be made from those shown in this figure. For instance, not all feature combinations lead to clearly distinguishable clusters. In this sample we include well-partitioned sets such as C3-C4, C5-C6, C7-C8, and some others where the data-points are mixed across classes, such as subspaces C1-C2 and C10-C11. Note also that although some data distribution may hint the existence of clusters, they may nonetheless be irrelevant because knowledge about one feature does not add insight about the other. That is the case of the C9-C10 subspace. Conversely, there are subspaces with a clear correlation between the data, but with indistinguishable clusters. That is the case of the C1-C2 subspace. These latter two types of subspaces do not contribute information to the clustering process \citep{Dy_2004_MLR}.

\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-05}
	\caption{A sample of the results from the multi-dimensional clustering analysis for pairs of consecutive metrics C1 through C11. These results are part of the 55 possible sub-spaces with 2 features (metrics). The cluster centers are shown with a cross symbol. Although for some pairs it may be obvious, the clusters 1 through 4 do not necessarily correspond in that order to the validation classes poor, fair, good, and excellent. The color version of this figure is available only in the electronic edition.}
	\label{fig:clusters}
\end{figure*}

@@

As a consequence, before moving on with the decision tree analysis, it is necessary to do resampling on the subset of the excellent class. In order to maintain a good number of samples for the other three classes, we used the oversampling approach described in the previous section. To that end, we replicated data randomly by a $\times$10 factor until elevating the number of samples in this class to 760 as indicated in Fig.~\ref{fig:count-classes}. By common standards, an oversample rate of $\times$10 is considered acceptable \textcolor{red}{(reference)}. (Arguably, we could have as well undersampled the fair class, but we deemed that unnecessary.) Once this process was completed we went on with the decision tree analysis.

>>>>

As explained in the methodology, the first step is to perform clustering process on the dataset in order to properly label the samples according to the classes to be used in the decision tree algorithm. Figure \ref{fig:clusters} presents a sample of the results obtained after the constrained \kmeans{} clustering process is completed, including subspacing. Recall that there are a total of 550 subspaces. Fig.~\ref{fig:clusters} shows three examples for each one of the types of subspaces, that is, three for each one of the 2-, 3-, and 4-feature analyses. However, since it is not practical or possible to present three- or higher-dimensional plots, we display the results from a two-dimensional perspective into the the subspaces by picking 2 metrics at a time. (Note that in the only cases in which this is a direct view into the clustering results is in the cases of the 2-feature analysis.)

% There are some characteristics of the results shown in Fig.~\ref{fig:clusters} worth

subspaces for an ordered sequence of metric pairs from C1 to C11 (see Table \ref{tab:metrics}). Although it would be impractical to discuss all the possible combinations, some points can be made from those shown in this figure. For instance, not all feature combinations lead to clearly distinguishable clusters. In this sample we include well-partitioned sets such as C3-C4, C5-C6, C7-C8, and some others where the data-points are mixed across classes, such as subspaces C1-C2 and C10-C11. Note also that although some data distribution may hint the existence of clusters, they may nonetheless be irrelevant because knowledge about one feature does not add insight about the other. That is the case of the C9-C10 subspace. Conversely, there are subspaces with a clear correlation between the data, but with indistinguishable clusters. That is the case of the C1-C2 subspace. These latter two types of subspaces do not contribute information to the clustering process \citep{Dy_2004_MLR}.

\begin{figure*}[ht!]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-05}
	\caption{A sample of the results from the multi-dimensional clustering analysis for pairs of consecutive metrics C1 through C11. These results are part of the 55 possible sub-spaces with 2 features (metrics). The cluster centers are shown with a cross symbol. Although for some pairs it may be obvious, the clusters 1 through 4 do not necessarily correspond in that order to the validation classes poor, fair, good, and excellent. The color version of this figure is available only in the electronic edition.}
	\label{fig:clusters}
\end{figure*}

@@

As a consequence, before moving on with the decision tree analysis, it is necessary to do resampling on the subset of the excellent class. In order to maintain a good number of samples for the other three classes, we used the oversampling approach described in the previous section. To that end, we replicated data randomly by a $\times$10 factor until elevating the number of samples in this class to 760 as indicated in Fig.~\ref{fig:count-classes}. By common standards, an oversample rate of $\times$10 is considered acceptable \citep{Weiss_2003_JAIR}. (Arguably, we could have as well undersampled the fair class, but we deemed that unnecessary.) Once this process was completed we went on with the decision tree analysis.
